---
title: "Descriptives: Helping Helpers (https://doi.org/10.1332/239788221X16535005914874)"
author: "Klara Raiber"
date: "June 2022"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r}
library(data.table)
library(tictoc)
library(kableExtra)
library(plyr)
library(foreign)
library(tidyr)
library(haven)
library(tidyverse)
library(magrittr)
library(beepr)
library(dplyr)
#library(XLConnect)
library(descr)
library(Rmisc)
library(plm)
library(pglm)
library(survival)
#library(xlsx)
library(ggpubr)
library(reshape)
```


#setup
```{r}
#working directory
setwd("U:/P1")
#check memory limit
memory.limit()
memory.limit(size = 6000000000000)
```
#load data sets
```{r}
#data for binary employment status
load("binary_outcome_data_for_comparison.dta") #bw_com
#subset for women
bw_wom <- subset(bw_com, bw_com$sex == 1) # 1 is women
#subset for men
bw_men <- subset(bw_com, bw_com$sex == 0) # 1 is women
#data for working hours
load("working_hours_data_for_comparison.dta") #wh_com
#subset for women
wh_wom <- subset(wh_com, wh_com$sex == 1) # 1 is women
#subset for men
wh_men <- subset(wh_com, wh_com$sex == 0) # 1 is women
```

######DESCRIPTIVE TABLE A1########
####BINARY EMPLOYMENT STATUS####
#caregiver per wave in binary employment status sample
```{r}
prop.table(table(bw_com$care_b,bw_com$wave), 2)
prop.table(table(bw_com$care,bw_com$wave), 2)

sub_care <- subset(bw_com, (bw_com$caregiver == 1 | bw_com$intense_care == 1))
prop.table(table(sub_care$intense_care))
```

#mt per wave in binary employment status sample
```{r}
prop.table(table(bw_com$mt_care,bw_com$wave), 2)
```

#number of respondents in binary employment status sample
```{r}
length(unique(bw_com$id)) # number of respondents
```

#####WOMEN FULL SAMPLE (BINARY EMPLOYMENT STATUS)######
#Number of respondents of women in binary employment status sample
```{r}
length(unique(bw_wom$id)) # number of respondents women
```

# binary employment of women in binary employment status sample
```{r}
prop.table(table(bw_wom$work_bi))
```

#caregiving of women in binary employment status sample
```{r}
prop.table(table(bw_wom$care))
```

#monetary transfers of women in binary employment status sample
```{r}
prop.table(table(bw_wom$mt_care))
```

#age of women in binary employment status sample
```{r}
mean(bw_wom$age)
sd(bw_wom$age)
```

#partner of women in binary employment status sample
```{r}
#single
prop.table(table(bw_wom$single))
#partner within the household
prop.table(table(bw_wom$partnerihh))
#partner outside the household
prop.table(table(bw_wom$partneroutside))
#partner missing
prop.table(table(bw_wom$partner_missing))
```

#children of women in binary employment status sample
```{r}
#no children under 15
prop.table(table(bw_wom$nochild))
#child under 4
prop.table(table(bw_wom$childu4))
#child under 15
prop.table(table(bw_wom$childu15))
```


#####MEN FULL SAMPLE (BINARY EMPLOYMENT STATUS)######
#Number of respondents of men in binary employment status sample
```{r}
length(unique(bw_men$id)) # number of respondents
```

# binary employment of men in binary employment status sample
```{r}
prop.table(table(bw_men$work_bi))
```

#caregiving of men in binary employment status sample
```{r}
prop.table(table(bw_men$care))
```

#monetary transfers of men in binary employment status sample
```{r}
prop.table(table(bw_men$mt_care))
```

#agein of men in binary employment status sample 
```{r}
mean(bw_men$age)
sd(bw_men$age)
```

#partner of men in binary employment status sample
```{r}
#single
prop.table(table(bw_men$single))
#partner within the householde
prop.table(table(bw_men$partnerihh))
#partner outside the household
prop.table(table(bw_men$partneroutside))
#partner missing
prop.table(table(bw_men$partner_missing))
```

#children of men in binary employment status sample
```{r}
#no children under 15
prop.table(table(bw_men$nochild))
#child under 4
prop.table(table(bw_men$childu4))
#child under 15
prop.table(table(bw_men$childu15))
```


#####WORKING HOURS#####
#number of respondents for working hours sample
```{r}
length(unique(wh_com$id)) # number of respondents
```

#####WOMEN WORKING HOURS SAMPLE######
#Number of respondents of women in working hours sample
```{r}
length(unique(wh_wom$id)) # number of respondents
```

#working hours of women in working hours sample
```{r}
mean(wh_wom$con_wo_ho)
sd(wh_wom$con_wo_ho)
```

#caregiving of women in working hours sample
```{r}
prop.table(table(wh_wom$care))
```

#monetary transfers of women in working hours sample
```{r}
prop.table(table(wh_wom$mt_care))
```

#age of women in working hours sample
```{r}
mean(wh_wom$age)
sd(wh_wom$age)
```

#partner of women in working hours sample
```{r}
#single
prop.table(table(wh_wom$single))
#partner within the householde
prop.table(table(wh_wom$partnerihh))
#partner outside the household
prop.table(table(wh_wom$partneroutside))
#partner missing
prop.table(table(wh_wom$partner_missing))
```

#children of women in working hours sample
```{r}
#no children under 15
prop.table(table(wh_wom$nochild))
#child under 4
prop.table(table(wh_wom$childu4))
#child under 15
prop.table(table(wh_wom$childu15))
```


#####MEN WORKING HOURS SAMPLE######
#Number of respondents of men in working hours sample
```{r}
length(unique(wh_men$id)) # number of respondents
```

#working hours of men in working hours sample
```{r}
mean(wh_men$con_wo_ho)
sd(wh_men$con_wo_ho)
```

#caregiving of men in working hours sample
```{r}
prop.table(table(wh_men$care))
```

#monetary transfers of men in working hours sample
```{r}
prop.table(table(wh_men$mt_care))
```

#age of men in working hours sample
```{r}
mean(wh_men$age)
sd(wh_men$age)
```

#partner of men in working hours sample
```{r}
#single
prop.table(table(wh_men$single))
#partner within the householde
prop.table(table(wh_men$partnerihh))
#partner outside the household
prop.table(table(wh_men$partneroutside))
#partner missing
prop.table(table(wh_men$partner_missing))
```

#children of men in working hours sample
```{r}
#no children under 15
prop.table(table(wh_men$nochild))
#child under 4
prop.table(table(wh_men$childu4))
#child under 15
prop.table(table(wh_men$childu15))
```



#####table A2 und A3 and preparation table 1#####
```{r}
#to wide format
bw_com.wide <- bw_com  %>% gather (key = variable, value = values, non_caregiver:high_to_non, -id, -wave)
bw_com.wide <- bw_com.wide %>% unite(variable.wave, variable, wave, sep = ".")
bw_com.wide <- bw_com.wide %>% spread(key = variable.wave, value = values)

#calculate changes in care for table 1
#to intense care
bw_com.wide$to_intense.2 <- NA
bw_com.wide$to_intense.3 <- ifelse(bw_com.wide$intense_care.2 == 0 &
                                       bw_com.wide$intense_care.3 == 1, 1, 0)
bw_com.wide$to_intense.4 <- ifelse(bw_com.wide$intense_care.3 == 0 &
                                       bw_com.wide$intense_care.4 == 1, 1, 0)
bw_com.wide$to_intense.5 <- ifelse(bw_com.wide$intense_care.4 == 0 &
                                       bw_com.wide$intense_care.5 == 1, 1, 0)
bw_com.wide$to_intense.6 <- ifelse(bw_com.wide$intense_care.5 == 0 &
                                       bw_com.wide$intense_care.6 == 1, 1, 0)
bw_com.wide$to_intense.7 <- ifelse(bw_com.wide$intense_care.6 == 0 &
                                       bw_com.wide$intense_care.7 == 1, 1, 0)
bw_com.wide$to_intense.8 <- ifelse(bw_com.wide$intense_care.7 == 0 &
                                       bw_com.wide$intense_care.8 == 1, 1, 0)
bw_com.wide$to_intense.9 <- ifelse(bw_com.wide$intense_care.8 == 0 &
                                       bw_com.wide$intense_care.9 == 1, 1, 0)
bw_com.wide$to_intense.10 <- ifelse(bw_com.wide$intense_care.9 == 0 &
                                       bw_com.wide$intense_care.10 == 1, 1, 0)
bw_com.wide$to_intense.11 <- ifelse(bw_com.wide$intense_care.10 == 0 &
                                       bw_com.wide$intense_care.11 == 1, 1, 0)
bw_com.wide$to_intense.12 <- ifelse(bw_com.wide$intense_care.11 == 0 &
                                       bw_com.wide$intense_care.12 == 1, 1, 0)
bw_com.wide$to_intense.13 <- ifelse(bw_com.wide$intense_care.12 == 0 &
                                       bw_com.wide$intense_care.13 == 1, 1, 0)

#to (non-intense) care
bw_com.wide$to_caregiver.2 <- NA
bw_com.wide$to_caregiver.3 <- ifelse(bw_com.wide$caregiver.2 == 0 &
                                       bw_com.wide$caregiver.3 == 1, 1, 0)
bw_com.wide$to_caregiver.4 <- ifelse(bw_com.wide$caregiver.3 == 0 &
                                       bw_com.wide$caregiver.4 == 1, 1, 0)
bw_com.wide$to_caregiver.5 <- ifelse(bw_com.wide$caregiver.4 == 0 &
                                       bw_com.wide$caregiver.5 == 1, 1, 0)
bw_com.wide$to_caregiver.6 <- ifelse(bw_com.wide$caregiver.5 == 0 &
                                       bw_com.wide$caregiver.6 == 1, 1, 0)
bw_com.wide$to_caregiver.7 <- ifelse(bw_com.wide$caregiver.6 == 0 &
                                       bw_com.wide$caregiver.7 == 1, 1, 0)
bw_com.wide$to_caregiver.8 <- ifelse(bw_com.wide$caregiver.7 == 0 &
                                       bw_com.wide$caregiver.8 == 1, 1, 0)
bw_com.wide$to_caregiver.9 <- ifelse(bw_com.wide$caregiver.8 == 0 &
                                       bw_com.wide$caregiver.9 == 1, 1, 0)
bw_com.wide$to_caregiver.10 <- ifelse(bw_com.wide$caregiver.9 == 0 &
                                       bw_com.wide$caregiver.10 == 1, 1, 0)
bw_com.wide$to_caregiver.11 <- ifelse(bw_com.wide$caregiver.10 == 0 &
                                       bw_com.wide$caregiver.11 == 1, 1, 0)
bw_com.wide$to_caregiver.12 <- ifelse(bw_com.wide$caregiver.11 == 0 &
                                       bw_com.wide$caregiver.12 == 1, 1, 0)
bw_com.wide$to_caregiver.13 <- ifelse(bw_com.wide$caregiver.12 == 0 &
                                       bw_com.wide$caregiver.13 == 1, 1, 0)

#to non-caregiving
bw_com.wide$to_non_caregiver.2 <- NA
bw_com.wide$to_non_caregiver.3 <- ifelse(bw_com.wide$non_caregiver.2 == 0 &
                                       bw_com.wide$non_caregiver.3 == 1, 1, 0)
bw_com.wide$to_non_caregiver.4 <- ifelse(bw_com.wide$non_caregiver.3 == 0 &
                                       bw_com.wide$non_caregiver.4 == 1, 1, 0)
bw_com.wide$to_non_caregiver.5 <- ifelse(bw_com.wide$non_caregiver.4 == 0 &
                                       bw_com.wide$non_caregiver.5 == 1, 1, 0)
bw_com.wide$to_non_caregiver.6 <- ifelse(bw_com.wide$non_caregiver.5 == 0 &
                                       bw_com.wide$non_caregiver.6 == 1, 1, 0)
bw_com.wide$to_non_caregiver.7 <- ifelse(bw_com.wide$non_caregiver.6 == 0 &
                                       bw_com.wide$non_caregiver.7 == 1, 1, 0)
bw_com.wide$to_non_caregiver.8 <- ifelse(bw_com.wide$non_caregiver.7 == 0 &
                                       bw_com.wide$non_caregiver.8 == 1, 1, 0)
bw_com.wide$to_non_caregiver.9 <- ifelse(bw_com.wide$non_caregiver.8 == 0 &
                                       bw_com.wide$non_caregiver.9 == 1, 1, 0)
bw_com.wide$to_non_caregiver.10 <- ifelse(bw_com.wide$non_caregiver.9 == 0 &
                                       bw_com.wide$non_caregiver.10 == 1, 1, 0)
bw_com.wide$to_non_caregiver.11 <- ifelse(bw_com.wide$non_caregiver.10 == 0 &
                                       bw_com.wide$non_caregiver.11 == 1, 1, 0)
bw_com.wide$to_non_caregiver.12 <- ifelse(bw_com.wide$non_caregiver.11 == 0 &
                                       bw_com.wide$non_caregiver.12 == 1, 1, 0)
bw_com.wide$to_non_caregiver.13 <- ifelse(bw_com.wide$non_caregiver.12 == 0 &
                                       bw_com.wide$non_caregiver.13 == 1, 1, 0)

#calculate change of employment status
bw_com.wide$change_bw.2 <- NA
bw_com.wide$change_bw.3 <- as.numeric(bw_com.wide$work_bi.2) -
  as.numeric(bw_com.wide$work_bi.3)
bw_com.wide$change_bw.4 <- as.numeric(bw_com.wide$work_bi.3) -
  as.numeric(bw_com.wide$work_bi.4)
bw_com.wide$change_bw.5 <- as.numeric(bw_com.wide$work_bi.4) -
  as.numeric(bw_com.wide$work_bi.5)
bw_com.wide$change_bw.6 <- as.numeric(bw_com.wide$work_bi.5) -
  as.numeric(bw_com.wide$work_bi.6)
bw_com.wide$change_bw.7 <- as.numeric(bw_com.wide$work_bi.6) -
  as.numeric(bw_com.wide$work_bi.7)
bw_com.wide$change_bw.8 <- as.numeric(bw_com.wide$work_bi.7) -
  as.numeric(bw_com.wide$work_bi.8)
bw_com.wide$change_bw.9 <- as.numeric(bw_com.wide$work_bi.8) -
  as.numeric(bw_com.wide$work_bi.9)
bw_com.wide$change_bw.10 <- as.numeric(bw_com.wide$work_bi.9) -
  as.numeric(bw_com.wide$work_bi.10)
bw_com.wide$change_bw.11 <- as.numeric(bw_com.wide$work_bi.10) -
  as.numeric(bw_com.wide$work_bi.11)
bw_com.wide$change_bw.12 <- as.numeric(bw_com.wide$work_bi.11) -
  as.numeric(bw_com.wide$work_bi.12)
bw_com.wide$change_bw.13 <- as.numeric(bw_com.wide$work_bi.12) -
  as.numeric(bw_com.wide$work_bi.13)


#lable: -1 is change from non-employed to employed, 1 is change from employed to non-employed
bw_com.wide$change_bw.3 <- recode(bw_com.wide$change_bw.3 , "-1" = 
                                    "non-employed to employed",
                                  "0" = "stable", "1" = "employed to non-employed")
bw_com.wide$change_bw.4 <- recode(bw_com.wide$change_bw.4 , "-1" = 
                                    "non-employed to employed",
                                  "0" = "stable", "1" = "employed to non-employed")
bw_com.wide$change_bw.5 <- recode(bw_com.wide$change_bw.5 , "-1" = 
                                    "non-employed to employed",
                                  "0" = "stable", "1" = "employed to non-employed")
bw_com.wide$change_bw.6 <- recode(bw_com.wide$change_bw.6 , "-1" = 
                                    "non-employed to employed",
                                  "0" = "stable", "1" = "employed to non-employed")
bw_com.wide$change_bw.7 <- recode(bw_com.wide$change_bw.7 , "-1" = 
                                    "non-employed to employed",
                                  "0" = "stable", "1" = "employed to non-employed")
bw_com.wide$change_bw.8 <- recode(bw_com.wide$change_bw.8 , "-1" = 
                                    "non-employed to employed",
                                  "0" = "stable", "1" = "employed to non-employed")
bw_com.wide$change_bw.9 <- recode(bw_com.wide$change_bw.9 , "-1" = 
                                    "non-employed to employed",
                                  "0" = "stable", "1" = "employed to non-employed")
bw_com.wide$change_bw.10 <- recode(bw_com.wide$change_bw.10 , "-1" = 
                                     "non-employed to employed",
                                  "0" = "stable", "1" = "employed to non-employed")
bw_com.wide$change_bw.11 <- recode(bw_com.wide$change_bw.11 , "-1" = 
                                     "non-employed to employed",
                                  "0" = "stable", "1" = "employed to non-employed")
bw_com.wide$change_bw.12 <- recode(bw_com.wide$change_bw.12 , "-1" = 
                                     "non-employed to employed",
                                  "0" = "stable", "1" = "employed to non-employed")
bw_com.wide$change_bw.13 <- recode(bw_com.wide$change_bw.13 , "-1" = 
                                     "non-employed to employed",
                                  "0" = "stable", "1" = "employed to non-employed")

#frequencies for table A2 - employment
prop.table(table(bw_com.wide$change_bw.3))
prop.table(table(bw_com.wide$change_bw.4))
prop.table(table(bw_com.wide$change_bw.5))
prop.table(table(bw_com.wide$change_bw.6))
prop.table(table(bw_com.wide$change_bw.7))
prop.table(table(bw_com.wide$change_bw.8))
prop.table(table(bw_com.wide$change_bw.9))
prop.table(table(bw_com.wide$change_bw.10))
prop.table(table(bw_com.wide$change_bw.11))
prop.table(table(bw_com.wide$change_bw.12))
prop.table(table(bw_com.wide$change_bw.13))

#Number of observations  for table A2
length(which(!is.na(bw_com.wide$change_bw.3)))
length(which(!is.na(bw_com.wide$change_bw.4)))
length(which(!is.na(bw_com.wide$change_bw.5)))
length(which(!is.na(bw_com.wide$change_bw.6)))
length(which(!is.na(bw_com.wide$change_bw.7)))
length(which(!is.na(bw_com.wide$change_bw.8)))
length(which(!is.na(bw_com.wide$change_bw.9)))
length(which(!is.na(bw_com.wide$change_bw.10)))
length(which(!is.na(bw_com.wide$change_bw.11)))
length(which(!is.na(bw_com.wide$change_bw.12)))
length(which(!is.na(bw_com.wide$change_bw.13)))

#caculate change for care
bw_com.wide$change_care.10 <- as.numeric(bw_com.wide$care_num.9) - 
  as.numeric(bw_com.wide$care_num.10)
bw_com.wide$change_care.11 <- as.numeric(bw_com.wide$care_num.10) -
  as.numeric(bw_com.wide$care_num.11)
bw_com.wide$change_care.12 <- as.numeric(bw_com.wide$care_num.11) -
  as.numeric(bw_com.wide$care_num.12)
bw_com.wide$change_care.13 <- as.numeric(bw_com.wide$care_num.12) -
  as.numeric(bw_com.wide$care_num.13)
bw_com.wide$change_care.2 <- NA
bw_com.wide$change_care.3 <- as.numeric(bw_com.wide$care_num.2) -
  as.numeric(bw_com.wide$care_num.3)
bw_com.wide$change_care.4 <- as.numeric(bw_com.wide$care_num.3) -
  as.numeric(bw_com.wide$care_num.4)
bw_com.wide$change_care.5 <- as.numeric(bw_com.wide$care_num.4) -
  as.numeric(bw_com.wide$care_num.5)
bw_com.wide$change_care.6 <- as.numeric(bw_com.wide$care_num.5) -
  as.numeric(bw_com.wide$care_num.6)
bw_com.wide$change_care.7 <- as.numeric(bw_com.wide$care_num.6) -
  as.numeric(bw_com.wide$care_num.7)
bw_com.wide$change_care.8 <- as.numeric(bw_com.wide$care_num.7) -
  as.numeric(bw_com.wide$care_num.8)
bw_com.wide$change_care.9 <- as.numeric(bw_com.wide$care_num.8) -
  as.numeric(bw_com.wide$care_num.9)


# positive is a change towards less caregiving
#negative is a change towards more caregiving
bw_com.wide$change_care.3 <- recode(bw_com.wide$change_care.3 , "-1" = 
                                      "more caregiving", 
                                    "-2" = "more caregiving", "0" = "stable", "1" = 
                                      "less caregiving", "2" = "less caregiving")
bw_com.wide$change_care.4 <- recode(bw_com.wide$change_care.4 , "-1" = 
                                      "more caregiving", 
                                    "-2" = "more caregiving", "0" = "stable", "1" = 
                                      "less caregiving", "2" = "less caregiving")
bw_com.wide$change_care.5 <- recode(bw_com.wide$change_care.5 , "-1" = 
                                      "more caregiving", 
                                    "-2" = "more caregiving", "0" = "stable", "1" = 
                                      "less caregiving", "2" = "less caregiving")
bw_com.wide$change_care.6 <- recode(bw_com.wide$change_care.6 , "-1" = 
                                      "more caregiving", 
                                    "-2" = "more caregiving", "0" = "stable", "1" = 
                                      "less caregiving", "2" = "less caregiving")
bw_com.wide$change_care.7 <- recode(bw_com.wide$change_care.7 , "-1" = 
                                      "more caregiving", 
                                    "-2" = "more caregiving", "0" = "stable", "1" = 
                                      "less caregiving", "2" = "less caregiving")
bw_com.wide$change_care.8 <- recode(bw_com.wide$change_care.8 , "-1" = 
                                      "more caregiving", 
                                    "-2" = "more caregiving", "0" = "stable", "1" = 
                                      "less caregiving", "2" = "less caregiving")
bw_com.wide$change_care.9 <- recode(bw_com.wide$change_care.9 , "-1" = 
                                      "more caregiving", 
                                    "-2" = "more caregiving", "0" = "stable", "1" = 
                                      "less caregiving", "2" = "less caregiving")
bw_com.wide$change_care.10 <- recode(bw_com.wide$change_care.10 , "-1" = 
                                       "more caregiving", 
                                    "-2" = "more caregiving", "0" = "stable", "1" = 
                                      "less caregiving", "2" = "less caregiving")
bw_com.wide$change_care.11 <- recode(bw_com.wide$change_care.11 , "-1" = 
                                       "more caregiving", 
                                    "-2" = "more caregiving", "0" = "stable", "1" = 
                                      "less caregiving", "2" = "less caregiving")
bw_com.wide$change_care.12 <- recode(bw_com.wide$change_care.12 , "-1" = 
                                       "more caregiving", 
                                    "-2" = "more caregiving", "0" = "stable", "1" = 
                                      "less caregiving", "2" = "less caregiving")
bw_com.wide$change_care.13 <- recode(bw_com.wide$change_care.13 , "-1" = 
                                       "more caregiving", 
                                    "-2" = "more caregiving", "0" = "stable", "1" = 
                                      "less caregiving", "2" = "less caregiving")

#frequencies for table A2
prop.table(table(bw_com.wide$change_care.3))
prop.table(table(bw_com.wide$change_care.4))
prop.table(table(bw_com.wide$change_care.5))
prop.table(table(bw_com.wide$change_care.6))
prop.table(table(bw_com.wide$change_care.7))
prop.table(table(bw_com.wide$change_care.8))
prop.table(table(bw_com.wide$change_care.9))
prop.table(table(bw_com.wide$change_care.10))
prop.table(table(bw_com.wide$change_care.11))
prop.table(table(bw_com.wide$change_care.12))
prop.table(table(bw_com.wide$change_care.13))



#save
save(bw_com.wide, file="bw_com.wide.dta")

#make data set smaller keeping only relevant variables
load("bw_com.wide.dta")
bw_com.wide <- subset(bw_com.wide, select = c(id, age.3, age.4, age.5, age.6, age.7, age.8, age.9, age.10, age.11, age.12, age.13, change_bw.3, change_bw.4, change_bw.5, change_bw.6, change_bw.7, change_bw.8, change_bw.9, change_bw.10, change_bw.11, change_bw.12, change_bw.13, to_caregiver.3, to_caregiver.4, to_caregiver.5, to_caregiver.6, to_caregiver.7, to_caregiver.8, to_caregiver.9, to_caregiver.10, to_caregiver.11, to_caregiver.12, to_caregiver.13, to_intense.3, to_intense.4, to_intense.5, to_intense.6, to_intense.7, to_intense.8, to_intense.9, to_intense.10, to_intense.11, to_intense.12, to_intense.13, to_non_caregiver.3, to_non_caregiver.4, to_non_caregiver.5, to_non_caregiver.6, to_non_caregiver.7, to_non_caregiver.8, to_non_caregiver.9, to_non_caregiver.10, to_non_caregiver.11, to_non_caregiver.12, to_non_caregiver.13, change_care.3, change_care.4, change_care.5, change_care.6, change_care.7, change_care.8, change_care.9, change_care.10, change_care.11, change_care.12, change_care.13))


#back to long format

bw_com.change <- melt(bw_com.wide, varying = NULL, id.vars = c("id"), vare_name = "wave")
bw_com.change <-  separate(bw_com.change, col = "variable", into = c("variable", "wave"), sep = "\\.")
bw_com.change <-spread(bw_com.change, key = "variable", value = "value")

#reduce to regular number of observation (exclude NA)
bw_com.change <- subset(bw_com.change, !(is.na(age)))


```
#Rest Table A2
```{r}
prop.table(table(bw_com.change$change_bw)) # averages
length(which(!is.na(w_com.change$change_bw))) # all observations together
prop.table(table(bw_com.change$change_care)) #averages

```



#####Table 1: Changes in care by changes in employment for succeeding years (in percentages)####
```{r}


#towards (non-intensive) care
table(bw_com.change$change_bw)
table(bw_com.change$to_caregiver)
table(bw_com.change$to_caregiver, bw_com.change$change_bw)
prop.table(table(bw_com.change$to_caregiver, bw_com.change$change_bw),1)
#towards intensive 
table(bw_com.change$to_intense)
table(bw_com.change$to_intense, bw_com.change$change_bw)
prop.table(table(bw_com.change$to_intense, bw_com.change$change_bw),1)
#towards non-caregiving
table(bw_com.change$to_non_caregiver)
table(bw_com.change$to_non_caregiver, bw_com.change$change_bw)
prop.table(table(bw_com.change$to_non_caregiver, bw_com.change$change_bw),1)
#stable
bw_com.change$stable <- ifelse(bw_com.change$to_caregiver == 0 & bw_com.change$to_intense ==
                                 0 & bw_com.change$to_non_caregiver == 0, 1, 0)
table(bw_com.change$stable)
table(bw_com.change$stable, bw_com.change$change_bw)
prop.table(table(bw_com.change$stable, bw_com.change$change_bw),1)
```

# care at least once 
```{r}
###EMPLOYMENT STATUS###
#save within variation on care
within_vars <- data.frame(tapply(bw_com$non_caregiver, bw_com$id, sd))
#get mean of variation
mean_care <- data.frame(tapply(bw_com$non_caregiver, bw_com$id, mean))
#get all that care more than once
mean_care_2 <- data.frame(mean_care[which(mean_care$tapply.bw_com.non_caregiver..bw_com.id..mean.<1),])
#respondents that care at least once
count(mean_care_2) 
#proportion of respondents that care at least once
count(mean_care_2)/count(mean_care) #16%

####WORKING HOURS####
#save within variation on care
within_vars_wh <- data.frame(tapply(wh_com$non_caregiver, wh_com$id, sd))
#get mean of variation
mean_care_wh <- data.frame(tapply(wh_com$non_caregiver, wh_com$id, mean))
#get all that care more than once
mean_care_2_wh <- data.frame(mean_care_wh[which(mean_care_wh$tapply.wh_com.non_caregiver..wh_com.id..mean.<1),]) 
#respondents that care at least once
count(mean_care_2_wh) 
#proportion of respondents that care at least once
count(mean_care_2_wh)/count(mean_care_wh)
```

# receives monetary transfers 
```{r}
#subset to only those that care
bw_carer <- subset(bw_com, bw_com$care_b == 1)
#how many of those that care receive monetary transfers
prop.table(table(bw_carer$mt_care, bw_carer$wave),2)
#mean monetary transfers of those that care
mean(bw_carer$mt2)
#mean of monetary transfers by intensity 
tapply(bw_carer$mt2, bw_carer$care, mean)
#mean of monetary transfers by employment status
tapply(bw_carer$mt2, bw_carer$work_bi, mean)
#mean of monetary transfers by sex
tapply(bw_carer$mt2, bw_carer$sex, mean)

#Check age of people with low MTs
newdata <- bw_carer[ which(bw_carer$mt <= 157),]
mean(newdata$age)
#Check age of people with high MTs
newdata_2 <- bw_carer[ which(bw_carer$mt > 157),]
mean(newdata_2$age)

#subset to those that receive MTs
bw_mt <- subset(bw_carer, bw_carer$mt2 > 0)
#summary receiving MTs
tapply(bw_mt$mt2, bw_mt$wave, summary)
#mean of those that receive MTs
tapply(bw_mt$mt2, bw_mt$wave, mean)
#median of those that receive MTs
tapply(bw_mt$mt2, bw_mt$wave, median)
```

#plotting descriptives
#graph on binary employment status with care 
```{r}
#prepare 
bw_com$work_bi <- as.numeric(bw_com$work_bi)
bw_com$sex <- as.factor(bw_com$sex)

#label sex
bw_com$Sex[bw_com$sex == 0] <- "Men"
bw_com$Sex[bw_com$sex == 1] <- "Women"


#change to British spelling
bw_com$Care <- as.character(ifelse(bw_com$care == 'Non-caregiver', 'Non-carer', bw_com$care))
bw_com$Care <- as.character(ifelse(bw_com$care == 'Non-intensive Caregiver', 'Non-intensive carer', bw_com$Care))
bw_com$Care <- as.character(ifelse(bw_com$care == 'Intensive caregiver', 'Intensive carer', bw_com$Care))



#calculate frequencies per group
w3 <- summarySE(bw_com, measurevar="work_bi", groupvars=c("Care", "Sex"), na.rm = TRUE)
table(w3$Care)

#plot
care_work_bi  <- ggplot(w3, aes(Sex, work_bi)) +   
  geom_bar(aes(fill = Care), width = 0.5, position = "dodge", stat="identity") +
  labs(x ="", y = "Percentage employed", shape="Care") +
  theme_set(theme_classic()) +
  scale_fill_manual(values= c("darkgrey", "darkslategrey", "black")) +
                      theme(text = element_text(size = 20))
#have a look
care_work_bi

#save
ggsave(care_work_bi, filename = "care_work_bi.jpg",
       device = "jpg", width = 20 , height = 14,
       units = "cm", dpi = 500)

#chisquare for descriptive differences
chisq.test(bw_wom$work_bi, bw_wom$care, correct=FALSE)
chisq.test(bw_men$work_bi, bw_men$care, correct=FALSE)

```

#graph on employment status per MT
```{r}
#prepare
bw_com$work_bi <- as.numeric(bw_com$work_bi)
bw_com$sex <- as.factor(bw_com$sex)

#lable sex
bw_com$Sex[bw_com$sex == 0] <- "Men"
bw_com$Sex[bw_com$sex == 1] <- "Women"

#change to British spelling
bw_com$Mt_care <- as.character(ifelse(bw_com$mt_care == 'Non-caregiver', 'Non-carer', bw_com$mt_care))
bw_com$Mt_care <- as.character(ifelse(bw_com$mt_care == 'Caregiver without mt', 'Carer without mt', bw_com$Mt_care))
bw_com$Mt_care <- as.character(ifelse(bw_com$mt_care == 'Caregiver with low mt', 'Carer with low mt', bw_com$Mt_care))
bw_com$Mt_care <- as.character(ifelse(bw_com$mt_care == 'Caregiver with high mt', 'Carer with high mt', bw_com$Mt_care))




#calculate frequencies per group
w3 <- summarySE(bw_com, measurevar="work_bi", groupvars=c("Mt_care", "Sex"), na.rm = TRUE)


#plot
mt_work_bi  <- ggplot(w3, aes(Sex, work_bi)) +   
  geom_bar(aes(fill = Mt_care), width = 0.5, position = "dodge", stat="identity") +
  labs(x ="", y = "Percentage employed", fill="Monetary Transfers (mt)") +
  theme_set(theme_classic()) +  
  scale_fill_manual(values= c("darkgrey", "darkslategrey", "grey39", "black"))+
                      theme(text = element_text(size = 20))
#have a look
mt_work_bi

#save
ggsave(mt_work_bi, filename = "mt_work_bi.jpg",
       device = "jpg", width = 20 , height = 14,
       units = "cm", dpi = 500)

#chi-sqaure test
chisq.test(bw_wom$work_bi, bw_wom$mt_care, correct=FALSE)
chisq.test(bw_men$work_bi, bw_men$mt_care, correct=FALSE)
```

#graph on working hours and care
```{r}
#label sex
wh_com$Sex[wh_com$sex == 0] <- "Men"
wh_com$Sex[wh_com$sex == 1] <- "Women"


#change to British spelling
wh_com$Care <- as.character(ifelse(wh_com$care == 'Non-caregiver', 'Non-carer', wh_com$care))
wh_com$Care <- as.character(ifelse(wh_com$care == 'Non-intensive Caregiver', 'Non-intensive carer', wh_com$Care))
wh_com$Care <- as.character(ifelse(wh_com$care == 'Intensive caregiver', 'Intensive carer', wh_com$Care))


#calculate differences per group
w_3 <- summarySE(wh_com, measurevar="con_wo_ho", groupvars=c("Care", "Sex"), na.rm = TRUE)
table(w_3)

#plot
care_con_wo_ho  <- ggplot(w_3, aes(Sex, con_wo_ho)) +   
  geom_bar(aes(fill = Care), width = 0.5, position = "dodge", stat="identity") +
  labs(x ="", y = "Average working hours", shape="Care") +
  theme_set(theme_classic()) +
  scale_fill_manual(values= c("darkgrey", "darkslategrey", "black")) +
                      theme(text = element_text(size = 20))
#have a look
care_con_wo_ho

#save
ggsave(care_con_wo_ho, filename = "care_con_wo_ho.jpg",
       device = "jpg", width = 20 , height = 14,
       units = "cm", dpi = 500)

#chi square test
chisq.test(wh_wom$con_wo_ho, wh_wom$care, correct=FALSE)
chisq.test(wh_men$con_wo_ho, wh_men$care, correct=FALSE)

```

#graph on working hours and MT
```{r}
#lable sex
wh_com$Sex[wh_com$sex == 0] <- "Men"
wh_com$Sex[wh_com$sex == 1] <- "Women"


#change to British spelling
wh_com$Mt_care <- as.character(ifelse(wh_com$mt_care == 'Non-caregiver', 'Non-carer', wh_com$mt_care))
wh_com$Mt_care <- as.character(ifelse(wh_com$mt_care == 'Caregiver without mt', 'Carer without mt', wh_com$Mt_care))
wh_com$Mt_care <- as.character(ifelse(wh_com$mt_care == 'Caregiver with low mt', 'Carer with low mt', wh_com$Mt_care))
wh_com$Mt_care <- as.character(ifelse(wh_com$mt_care == 'Caregiver with high mt', 'Carer with high mt', wh_com$Mt_care))


#calculate frequencies per group
w_4 <- summarySE(wh_com, measurevar="con_wo_ho", groupvars=c("Mt_care", "Sex"), na.rm = TRUE)
table(w_4)

#plot
mt_con_wo_ho  <- ggplot(w_4, aes(Sex, con_wo_ho)) +   
  geom_bar(aes(fill = Mt_care), width = 0.5, position = "dodge", stat="identity") +
  labs(x ="", y = "Average working hours", fill="Monetary Transfers (mt)") +
  theme_set(theme_classic()) +
  scale_fill_manual(values= c("darkgrey", "darkslategrey", "grey39", "black")) +
                      theme(text = element_text(size = 20))
#have a look
mt_con_wo_ho

#save
ggsave(mt_con_wo_ho, filename = "mt_con_wo_ho.jpg",
       device = "jpg", width = 20 , height = 14,
       units = "cm", dpi = 500)

#Test for group differences 
chisq.test(wh_wom$con_wo_ho, wh_wom$mt_care, correct=FALSE)
chisq.test(wh_men$con_wo_ho, wh_men$mt_care, correct=FALSE)
```

#putting graphs together: FIGURE 1 & 2
```{r}
#####CARE - FIGURE 1 #####
graphs_on_care <- ggarrange(care_work_bi, care_con_wo_ho,
                    ncol = 2, nrow = 1,
common.legend = TRUE, legend = "right")
graphs_on_care

#save
ggsave(graphs_on_care, filename = "graphs_on_care.eps",
       device = "eps", width = 25, height = 10,
       units = "cm", dpi = 500)

#####Monetary transfers - FIGURE 2####
graphs_on_mt <- ggarrange(mt_work_bi, mt_con_wo_ho,
                    ncol = 2, nrow = 1,
common.legend = TRUE, legend = "right")
graphs_on_mt

#save
ggsave(graphs_on_mt, filename = "graphs_on_mt.eps",
       device = "eps", width = 25, height = 10,
       units = "cm", dpi = 500)
```

