---
title: "Robustness checks: Helping Helpers (https://doi.org/10.1332/239788221X16535005914874)"
author: "Klara Raiber"
date: "June 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Setup
```{r}
#working directory
setwd("U:/P1")
#check memory limit
memory.limit()
memory.limit(size = 6000000000000)
```

#Packages
```{r}
library(data.table)
library(kableExtra)
library(plyr)
library(foreign)
library(tidyr)
library(haven)
library(tidyverse)
library(magrittr)
library(dplyr)
library(descr)
library(Rmisc)
library(plm)
library(survival)
library(stargazer)
library(jtools)
library(huxtable)
library(tictoc)
library(bife)
```


#load datasets
```{r}
#data for comparison
load("actuel_working_hours_data_for_comparison.dta") 
load("binary_outcome_data_for_comparison.dta")
load("working_hours_data_for_comparison.dta")

#subset for women
bw_wom <- subset(bw_com, bw_com$sex == 1) # 1 is women
#subset for men
bw_men <- subset(bw_com, bw_com$sex == 0) # 1 is women
```

#check results for actual working hours
```{r}
#load data  
load("actuel_working_hours_data_for_comparison.dta")

#subset
wh_men_act <- subset(wh_com_act, wh_com_act$sex == 0) # 1 is women
wh_wom_act <- subset(wh_com_act, wh_com_act$sex == 1) # 1 is women

#Model: caregiving on actual working hours
#WOMEN
care_ac_wo_ho_wom <- plm(ac_wo_ho ~ caregiver + intense_care + age + age_sq +
                        partneroutside + partnerihh + partner_missing + nochild +
                        childu15 ,
                      data = wh_wom_act,
                      index = c("id", "wave"),
                      model = "within")
summary(care_ac_wo_ho_wom)

#MEN -intensive not anymore
care_ac_wo_ho_men <- plm(ac_wo_ho ~ caregiver + intense_care + age + age_sq +
                        partneroutside + partnerihh + partner_missing + nochild +
                          childu15 ,
                      data = wh_men_act,
                      index = c("id", "wave"),
                      model = "within")
summary(care_ac_wo_ho_men)


#Model: monetary transfers on actual working hours
#WOMEN - no low mt any more
mt_ac_wo_ho_wom <- plm(ac_wo_ho ~  non_caregiver + lowmt + highmt + age + age_sq +
                      partneroutside + partnerihh + partner_missing + nochild + 
                      childu15  ,
                    data = wh_wom_act,
                    index = c("id", "wave"),
                    model = "within")
summary(mt_ac_wo_ho_wom)

#MEN
mt_ac_wo_ho_men <- plm(ac_wo_ho ~  non_caregiver + lowmt + highmt + age + age_sq +
                      partneroutside + partnerihh + partner_missing + nochild + 
                      childu15  ,
                    data = wh_men_act,
                    index = c("id", "wave"),
                    model = "within")
summary(mt_ac_wo_ho_men)


#Model: caregiving x sex on actual working hours
care_ac_wo_ho_sex <- plm(ac_wo_ho ~ caregiver + intense_care + caregiver*sex +  intense_care*sex   + age + age_sq + partneroutside +  partnerihh + partner_missing +
                            nochild + childu15  ,
                          data = wh_com_act,
                          index = c("id", "wave"),
                      model = "within")
summary(care_ac_wo_ho_sex)

#Model 4: monetary transfers x sex on working hours
mt_ac_wo_ho_sex <- plm(ac_wo_ho ~ non_caregiver + lowmt + highmt +
                          non_caregiver * sex + lowmt*sex + highmt*sex + age + 
                          age_sq + partneroutside +  partnerihh + partner_missing +
                          nochild + childu15  ,
                        data = wh_com_act,
                        index = c("id", "wave"),
                        model = "within")
summary(mt_ac_wo_ho_sex)
```

#check influence of age restriction: narrowing down to age 18-55 on EMPLOYMENT OUTCOME
```{r}
#narrowing down to labor force 18-55
bw_restrict <- subset(bw_com, bw_com$age < 56) #select respondents from 18 on till 55 
bw_men_restrict <- subset(bw_restrict, bw_restrict$sex == 0) # 1 is women
bw_wom_restrict <- subset(bw_restrict, bw_restrict$sex == 1) # 1 is women

#Model: caregiving on employment status for age <= 55
#WOMEN
care_bi_em_res_wom <- bife(work_bi ~ caregiver + intense_care + age + age_sq 
                         + partneroutside + partnerihh  + partner_missing 
                         + nochild + childu15 | id, bw_wom_restrict, "logit")

care_bi_em_res_wom <- bias_corr(care_bi_em_res_wom) #bias correction
care_bi_em_res_wom <- get_APEs(care_bi_em_res_wom)
summary(care_bi_em_res_wom)

#MEN
care_bi_em_res_men <- bife(work_bi ~ caregiver + intense_care + age + age_sq 
                         + partneroutside + partnerihh  + partner_missing 
                         + nochild + childu15 | id, bw_men_restrict, "logit")

care_bi_em_res_men <- bias_corr(care_bi_em_res_men) #bias correction
care_bi_em_res_men <- get_APEs(care_bi_em_res_men)
summary(care_bi_em_res_men)


#Model: monetary transfers on employment status <= 55
#WOMEN
mt_bi_em_res_wom <- bife(work_bi ~ non_caregiver + lowmt + highmt + age 
                       + age_sq +  partneroutside + partnerihh  
                       + partner_missing + nochild + childu15 
                       | id, bw_wom_restrict, "logit")

mt_bi_em_res_wom <- bias_corr(mt_bi_em_res_wom) #bias correction
mt_bi_em_res_wom <- get_APEs(mt_bi_em_res_wom)
summary(mt_bi_em_res_wom)

#MEN
mt_bi_em_res_men <- bife(work_bi ~ non_caregiver + lowmt + highmt + age 
                       + age_sq +  partneroutside + partnerihh  
                       + partner_missing + nochild + childu15 
                       | id, bw_men_restrict, "logit")

mt_bi_em_res_men <- bias_corr(mt_bi_em_res_men) #bias correction
mt_bi_em_res_men <- get_APEs(mt_bi_em_res_men)
summary(mt_bi_em_res_men)


#Model: caregiving x sex on employment status <= 55
bw_restrict$caresex <- bw_restrict$caregiver * bw_restrict$sex
bw_restrict$intcaresex <- bw_restrict$intense_care * bw_restrict$sex

care_bi_em_sex_res <- bife(work_bi ~ caregiver + intense_care  + caresex +  intcaresex + age + age_sq +  partneroutside 
                         + partnerihh +  partner_missing  
                         + nochild + childu15   | id, bw_restrict, "logit")


care_bi_em_sex_res <- bias_corr(care_bi_em_sex_res) #bias correction
care_bi_em_sex_res <- get_APEs(care_bi_em_sex_res)
summary(care_bi_em_sex_res)


#Model: monetary transfers x sex on employment status <= 55

bw_restrict$noncaresex <- bw_restrict$non_caregiver * as.numeric(bw_restrict$sex)
bw_restrict$lowmtsex <- bw_restrict$lowmt * as.numeric(bw_restrict$sex)
bw_restrict$highmtsex <- bw_restrict$highmt * as.numeric(bw_restrict$sex)

mt_bi_em_sex_res <- bife(work_bi ~ non_caregiver + lowmt + highmt 
                       + noncaresex + lowmtsex
                       + highmtsex + age + age_sq +  partneroutside 
                       + partnerihh +  partner_missing  + nochild 
                       + childu15   | id, bw_restrict, "logit")

mt_bi_em_sex_res <- bias_corr(mt_bi_em_sex_res) #bias correction
mt_bi_em_sex_res <- get_APEs(mt_bi_em_sex_res)
summary(mt_bi_em_sex_res)

```


#check influence of age restriction: narrowing down to age 18-55 on WORKING HOURS
```{r}
#narrowing down to labor force 18-55
wh_restrict <- subset(wh_com, wh_com$age < 56) #select respondents from 18 on till 55 
wh_men_restrict <- subset(wh_restrict, wh_restrict$sex == 0) # 1 is women
wh_wom_restrict <- subset(wh_restrict, wh_restrict$sex == 1) # 1 is women

#Model: caregiving on working hours for age <= 55
#WOMEN
care_wh_res_wom <- plm(con_wo_ho ~ caregiver + intense_care + age + 
                               age_sq +  partneroutside + partnerihh  +
                               partner_missing + nochild + childu15 ,  
                       data = wh_wom_restrict,
                       index = c("id", "wave"),
                       model = "within")
summary(care_wh_res_wom)

#MEN
care_wh_res_men <- plm(con_wo_ho ~ caregiver + intense_care + age + 
                               age_sq +  partneroutside  + partnerihh  +
                               partner_missing + nochild + childu15  , 
                       data = wh_men_restrict,
                        index = c("id", "wave"),
                        model = "within")
summary(care_wh_res_men)


#Model: monetary transfers on working hours <= 55
#WOMEN
mt_wh_res_wom <- plm(con_wo_ho ~ non_caregiver + lowmt + highmt + age + 
                             age_sq +  partneroutside  + partnerihh  + 
                             partner_missing + nochild + childu15 ,
                     data = wh_wom_restrict,
                      index = c("id", "wave"),
                      model = "within")
summary(mt_wh_res_wom)

#MEN
mt_wh_res_men <- plm(con_wo_ho ~ non_caregiver + lowmt + highmt + age + 
                             age_sq +  partneroutside + partnerihh  + 
                             partner_missing + nochild + childu15 ,
                     data = wh_men_restrict,
                     index = c("id", "wave"),
                     model = "within")
summary(mt_wh_res_men)

#Model: caregiving x sex on working hours <= 55
care_wh_sex_res <- plm(con_wo_ho ~ caregiver + intense_care + caregiver*sex +
                         intense_care*sex + age + age_sq +  partneroutside +
                         partnerihh +  partner_missing  + nochild + childu15,  
                       data = wh_restrict,
                       index = c("id", "wave"),
                       model = "within") 
summary(care_wh_sex_res)

#Model: monetary transfers x sex on working hours <= 55
mt_wh_sex_res <- plm(con_wo_ho ~ non_caregiver + lowmt + highmt + non_caregiver * 
                     sex + lowmt * sex + highmt * sex + age + age_sq +  
                       partneroutside +  partnerihh +  partner_missing  + nochild + 
                       childu15 ,  
                     data = wh_restrict,
                     index = c("id", "wave"),
                     model = "within")
summary(mt_wh_sex_res)
```



#using a different cutpoint for intensive care (11 instead of 8) on EMPLOYMENT STATUS
```{r}
#sub-setting
bw_com$work_bi <- as.numeric(bw_com$work_bi)
bw_wom <- subset(bw_com, bw_com$sex == 1) # 1 is women
bw_men <- subset(bw_com, bw_com$sex == 0) # 1 is women

#Model: caregiving on employment status with 11 as cut-point
#WOMEN
care_bi_em_care11_wom <- bife(work_bi ~ caregiver_11 + intense_care_11 + age + age_sq 
                         + partneroutside + partnerihh  + partner_missing 
                         + nochild + childu15 | id, bw_wom, "logit")

summary(care_bi_em_care11_wom)

care_bi_em_care11_wom <- bias_corr(care_bi_em_care11_wom) #bias correction
summary(care_bi_em_care11_wom)
care_bi_em_care11_wom <- get_APEs(care_bi_em_care11_wom)
summary(care_bi_em_care11_wom)


#MEN
care_bi_em_care11_men <- bife(work_bi ~ caregiver_11 + intense_care_11 + age + age_sq 
                         + partneroutside + partnerihh  + partner_missing 
                         + nochild + childu15 | id, bw_men, "logit")

summary(care_bi_em_care11_men)

care_bi_em_care11_men <- bias_corr(care_bi_em_care11_men) #bias correction
summary(care_bi_em_care11_men)
care_bi_em_care11_men <- get_APEs(care_bi_em_care11_men)
summary(care_bi_em_care11_men)

#Model: caregiving x sex on employment status with 11 as cut-point
bw_com$caresex11 <- bw_com$caregiver_11 * bw_com$sex

bw_com$intcaresex11 <- bw_com$intense_care_11 * bw_com$sex

care_bi_em_sex_care11 <- bife(work_bi ~ caregiver_11 + intense_care_11  + caresex11 +  intcaresex11 + age + age_sq +  partneroutside 
                         + partnerihh +  partner_missing  
                         + nochild + childu15   | id, bw_com, "logit")

care_bi_em_sex_care11 <- bias_corr(care_bi_em_sex_care11) #bias correction
care_bi_em_sex_care11 <- get_APEs(care_bi_em_sex_care11)
summary(care_bi_em_sex_care11)
```

##using a different cutpoint for intensive care (11 instead of 8) ON WORKING HOURS
```{r}
#sub-setting
wh_men <- subset(wh_com, wh_com$sex == 0) # 1 is women
wh_wom <- subset(wh_com, wh_com$sex == 1) # 1 is women

#Model: caregiving on working hours with 11 as cut-point
#WOMEN
care_con_wo_ho_care11_wom <- plm(con_wo_ho ~ caregiver_11 + intense_care_11 + age +
                                   age_sq + partneroutside + partnerihh +
                                   partner_missing + nochild + childu15  , 
                                 data = wh_wom, 
                                 index = c("id", "wave"), 
                                 model = "within")
summary(care_con_wo_ho_care11_wom)

#MEN
care_con_wo_ho_care11_men <- plm(con_wo_ho ~ caregiver_11 + intense_care_11 + age +
                                   age_sq + partneroutside + partnerihh +
                                   partner_missing + nochild + childu15  , 
                                 data = wh_men, 
                                 index = c("id", "wave"), 
                                 model = "within")
summary(care_con_wo_ho_care11_men)

#Model caregiving x sex on working hours with 11 as cut-point
care_con_wo_ho_sex_care11 <- plm(con_wo_ho ~ caregiver_11 + intense_care_11 +
                                   caregiver_11*sex +  intense_care_11*sex   + age +
                                   age_sq + partneroutside +  partnerihh +
                                   partner_missing + nochild + childu15  , 
                                 data = wh_com, 
                                 index = c("id", "wave"), 
                                 model = "within")
summary(care_con_wo_ho_sex_care11)
```

#Checking oversampling of low-ses households on models on working hours
```{r}
#Model: caregiving x ses on working hours
#WOMEN
care_con_wo_ho_wom_ses <- plm(con_wo_ho ~ caregiver*ses_missing + caregiver*ses_low +
                                caregiver*ses_middle + intense_care*ses_missing +
                                intense_care*ses_low + intense_care*ses_middle + age +
                                age_sq + partneroutside + partnerihh + 
                                partner_missing + nochild + childu15  ,
                              data = wh_wom,
                              index = c("id", "wave"),
                              model = "within")
summary(care_con_wo_ho_wom_ses)

#MEN
care_con_wo_ho_men_ses <- plm(con_wo_ho ~ caregiver*ses_missing + caregiver*ses_low +
                                caregiver*ses_middle + intense_care*ses_missing + 
                                intense_care*ses_low + intense_care*ses_middle + age +
                                age_sq + partneroutside + partnerihh + 
                                partner_missing + nochild + childu15  ,
                              data = wh_men,
                              index = c("id", "wave"),
                              model = "within")
summary(care_con_wo_ho_men_ses)

#Model: monetary transfers x ses on working hours
#WOMEN
mt_con_wo_ho_wom_ses <- plm(con_wo_ho ~  non_caregiver*ses_missing + 
                              non_caregiver*ses_low + non_caregiver*ses_middle + 
                              lowmt*ses_missing + lowmt*ses_low + lowmt*ses_middle + 
                              highmt*ses_missing + highmt*ses_low + 
                              highmt*ses_middle + age + age_sq + partneroutside +
                              partnerihh + partner_missing + nochild + childu15 ,
                            data = wh_wom,
                            index = c("id", "wave"),
                            model = "within")
summary(mt_con_wo_ho_wom_ses)

#MEN
mt_con_wo_ho_men_ses <- plm(con_wo_ho ~  non_caregiver*ses_missing +
                              non_caregiver*ses_low + non_caregiver*ses_middle +
                              lowmt*ses_missing + lowmt*ses_low + lowmt*ses_middle +
                              highmt*ses_missing + highmt*ses_low + 
                              highmt*ses_middle + age + age_sq +
                              partneroutside + partnerihh + partner_missing + 
                              nochild + childu15 ,
                            data = wh_men, 
                            indqwex = c("id", "wave"), 
                            model = "within")
summary(mt_con_wo_ho_men_ses)

#Model 3: caregiving x ses x sex on working hours
care_con_wo_ho_sex_ses <- plm(con_wo_ho ~ caregiver*ses_missing + 
                                caregiver*ses_low + caregiver*ses_middle +
                                intense_care*ses_missing + intense_care*ses_low +
                                intense_care*ses_middle + caregiver*sex*ses_missing +
                                caregiver*sex*ses_low + caregiver*sex*ses_middle + 
                                intense_care*sex*ses_missing +
                                intense_care*sex*ses_low +
                                intense_care*sex*ses_middle + age + age_sq +
                                partneroutside +  partnerihh +
                                partner_missing + nochild + childu15  ,
                              data = wh_com,
                              index = c("id", "wave"),
                              model = "within")
summary(care_con_wo_ho_sex_ses)

#Model 4: monetary transfers x sex x ses on working hours
mt_con_wo_ho_sex_ses <- plm(con_wo_ho ~ non_caregiver*ses_missing +
                              non_caregiver*ses_low + non_caregiver*ses_middle +
                              lowmt*ses_missing + lowmt*ses_low + lowmt*ses_middle +
                              highmt*ses_missing + highmt*ses_low + 
                              highmt*ses_middle + non_caregiver * sex *ses_missing + 
                              non_caregiver * sex *ses_low + 
                              non_caregiver * sex *ses_middle +  
                              lowmt*sex *ses_missing + lowmt*sex *ses_low + 
                              lowmt*sex *ses_middle + highmt*sex*ses_missing + 
                              highmt*sex*ses_low + highmt*sex*ses_middle + age + 
                              age_sq + partneroutside +  partnerihh + 
                              partner_missing + nochild + childu15 ,
                          data = wh_com,
                          index = c("id", "wave"),
                          model = "within")
summary(mt_con_wo_ho_sex_ses)

```
